### 2019-02-20 experiments.tex
more on experiments

We also used {\tt redis-py} to investigate the tradeoff between
overhead and ability to detect nondeterminism when using the two
proposed approaches to horizontal determinism.  We produced 300 tests
of length 100, using the known-nondeterministic version of the {\tt
  redis-py} harness.  We then used {\tt nondeterministic} and {\tt
  stepNondeterministic} calls, both with a delay of 0.005 seconds and
a single additonal execution of the test, to
check these tests for nondeterministic behavior.  Final state
nondeterminism actually detected one instance of nondeterminism that
visible value nondeterminism failed to detect; in general, final state
nondeterminism is less able to detect nondeterminism, but in this
instance the difference is less important than the nondeterminism of
whether a particular test will exhibit nondeterministic behavior in a
single run.  This difference is obviously not statistically
significant; for the nondeterminism in {\tt redis-py}, with these
parameters, the two approaches cannot be statistically distinguished
as to effectiveness in detecting nondeterminism.

Final state nondeterminism was also faster; visible value
nondeterminism took, on average, 0.48\% longer to check for
nondeterminism on the 300 tests.  The difference was significant, with
$p$-value $< 1.19 \times 10^{-23}$ by a paired Wilcoxon test.

>>>>

We also used {\tt redis-py} to investigate the tradeoff between
overhead and ability to detect nondeterminism when using the two
proposed approaches to horizontal determinism.  We produced 300 tests
of length 100, using the known-nondeterministic version of the {\tt
  redis-py} harness.  We then used {\tt nondeterministic} and {\tt
  stepNondeterministic} calls, both with a delay of 0.005 seconds and
a single additonal execution of the test, to
check these tests for nondeterministic behavior.  Final state
nondeterminism actually detected one instance of nondeterminism that
visible value nondeterminism failed to detect (21 detections vs. 20); in general, final state
nondeterminism is less able to detect nondeterminism, but in this
instance the difference is less important than the nondeterminism of
whether a particular test will exhibit nondeterministic behavior in a
single run.  This difference is obviously not statistically
significant; for the nondeterminism in {\tt redis-py}, with these
parameters, the two approaches cannot be statistically distinguished
as to effectiveness in detecting nondeterminism.

Final state nondeterminism was also faster; visible value
nondeterminism took, on average, 0.48\% longer to check for
nondeterminism on the 300 tests, 1.199 mean seconds vs. 1.205 mean seconds.  The difference was significant, with
$p$-value $< 1.19 \times 10^{-23}$ by a paired Wilcoxon test.
